Effects of Unemployment Benefits and Uncertainty in Heterogeneous Models

### 2017-01-19 presentation/presentation.tex
Start
changes

>>>>

\begin{frame}{Adding aggregate uncertainty}
  \begin{itemize}

  \item {
  Aggregate uncertainty! Why?
  }
  \pause
  \item {
  Two aggregate productivity : $z \in \{ 0.99, 1.01 \}$.
  }

  \item {
  Two unemployment states: $L \in \{ 0.1, 0.4 \}$.
  }

  \item {
  2 transition matricies between employed and unemployed respectively in good and bad states and 1 transition matrix between good and bad state: $L \in \{ 0.1, 0.4 \}$.
  }

  \pause

  \item {
  Let's solve it!.
  }

  \end{itemize}

\end{frame}

\begin{frame}{Problem}
  \begin{itemize}

  \item {
  The introduction of aggregate uncertainty makes the distribution of wealth changing over time, which is infinite dimensional object.
  }

  \item {
  The capital distribution must be taken into account by the agents, therefore it becomes state variable.
  }

  \end{itemize}

\end{frame}

\begin{frame}{Solution}
  \begin{itemize}

  \item {
  There is no solution.
  }

  \item {
  Krusell and Smith (1997) suggest an algorithm to solve the issue by an approximation, which could be summerized as "rational adaptive expectations".
  }

  \item {
  They assume that the agents forecast prices by using the future mean of the wealth distribution.
  }

  \item {
  The actual forecast is made for the future mean based on previous realizations using some Least Squares technique.
  }

  \end{itemize}

\end{frame}

\begin{frame}{Algorithm}
  \begin{enumerate}

  \item {
  Draw shocks.
  }

  \item {
  Guess initial coefficients for the forcasting rule.  
  }

  \item {
  Solve the individual problem.
  }

  \item {
  Use the policy function to generate a sequence of capital distributions.
  }

  \item {
  The actual forecast is made for the future mean based on previous realizations using some Least Squares technique.
  }

  \item {
  Estimate new coefficients based on past realizations of the distribution and iterate until they converge. 
  }

  \end{enumerate}

\end{frame}
